Landau quantization of nearly degenerate bands, \\ and full symmetry classification of Landau-level crossings

### 2019-05-17 paper.tex
Updates from Overleaf

\begin{figure}
\includegraphics[width=1.0\columnwidth]{LL.png}
\caption{A schematic illustration of Landau level dispersion (solid lines) with respect to $B$ for nearly-degenerate orbits. For better illustration, we have exaggerated the change of $\delta\lambda$ with respect to $B$ and $E$. $\delta\lambda$ is plotted in the colored background. Landau level quasidegeneracies occur at $\delta\lambda\equiv 0$ ({indicated by red dashed lines}).\label{fig:LL}}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=1.0\columnwidth]{LL.png}
\caption{A schematic illustration of Landau level dispersion (solid lines) with respect to $B$ for nearly-degenerate orbits in 2DEG with Rashba and Dresselhaus spin orbit coupling [cf. Eq. (\ref{hamRD})]. For better illustration, the parameters have been chosen such that the change of $\delta\lambda$ with respect to $B$ and $E$ is exaggerated. $\delta\lambda$ is plotted in the colored background. Landau level quasidegeneracies occur at $\delta\lambda=0$ (indicated by red dashed lines) and $\delta\lambda=2\pi$ is never reached [cf. Sec. \ref{sec:singleparameterrashba}]. Parameters: $m=0.076m_0$, $\alpha=7.6\times 10^6$cm/s, $\beta=4.6\times 10^6$cm/s.\label{fig:LL}}
\end{figure}
